Constrained Natural Language Parser for Semantic Web Based Policies

### 2009-08-15 paper/paper.tex
some modifications to the introduction

The growth in the sheer volume and variety of information on the web
shows no signs of slowing down, and electronic information systems are
attracting a wider range of users than ever. Administrators of these
systems face a challenging task: determining and enforcing policies
for controlling the access of information.

Unfortunately, many of the existing systems do not posess the
capacity to keep up with the rapid expansion of the data set and the
user base. The functionality for policy enforcement is often built
into a system during its initial development. As a result, access
control in most of these systems is rather limited and inflexible to changes.
As a need for new policies arises or usage scenarios grow
more complex, the administrator may need to modify parts of the system
that are responsible for maintaining and enforcing the policies. This
can be a costly and error-prone process.

@@

We propose a potential solution to these challenges. Our prototype
system, called the Policy Parser, consists of two major parts:
(1) a graphical front-end, which translates an input natural language policy
into a set of RDF tuples, and (2) the Accountability In RDF (AIR)
reasoner, which automatically carries a series of logical
deductions to check whether a policy is enforced by a particular usage
scenario. The front-end uses templates to capture and extract
essential components of a policy and translate them into RDF tuples;
it can be easily extended with additional templates as the types of
policies diversify. Many forms of policy enforcement are
reducible to the logical reasoning that can be performed by the AIR
reasoner. Thus, even when policies undergo changes, the
underlying enforcement engine in our system need not be modified.

>>>>

The growth in the sheer volume and variety of information on the web
shows no signs of slowing down, and electronic information systems are
attracting a wider range of users than ever. There are lots of laws and policies which would often be useful if represented in a machine readable format rather than a verbose natural language description that nobody ever cares to read nor is able to understand. From an archival perspective, this would enable one to keep a repository of laws and policies.

In addition, administrators of these systems face a challenging task in determining and enforcing policies
for controlling the access of information. Unfortunately, many of the existing systems do not posess the
capacity to keep up with the rapid expansion of the data set and the
user base. The functionality for policy enforcement is often built
into a system during its initial development. As a result, access
control in most of these systems is rather limited and inflexible to changes.
As a need for new policies arises or usage scenarios grow
more complex, the administrator may need to modify parts of the system
that are responsible for maintaining and enforcing the policies. This
can be a costly and error-prone process.

@@

We propose a potential solution to these challenges. Our prototype
system, called the Policy Parser, consists of two major parts:
(1) a graphical front-end, which translates an input natural language policy
into a set of RDF triples, and (2) the Accountability In RDF (AIR)
reasoner, which automatically carries a series of logical
deductions to check whether a policy is enforced by a particular usage
scenario. The front-end uses templates to capture and extract
essential components of a policy and translate them into RDF triples;
it can be easily extended with additional templates as the types of
policies diversify. Many forms of policy enforcement are
reducible to the logical reasoning that can be performed by the AIR
reasoner. Thus, even when policies undergo changes, the
underlying enforcement engine in our system need not be modified.
